---
title: "Marriage Statistic"
author: 
  - Yitong Wang
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "The article is the data analysis for toronto marriage license, sctter plot included."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

```


# Introduction

We analysis the data of marriage license in Canada. We use @talia, @opendatatorotno, and @rohan.

The remainder of this paper is structured as follows. @sec-mydatasection



# Data {#sec-mydatasection}

Some of our data is of penguins (@fig-marriage), from @palmerpenguins.

```{r}
#| label: fig-marriage
#| fig-cap: Bills of penguins
#| echo: false

data |> 
  ggplot(aes(x = date, y = marriage_licenses)) +
  geom_point()

```
The scatter plot shows the relationship between the observation.



# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

Economic ups and downs, along with legal tweaks, really shake up how many folks decide to tie the knot. Spotting these trends helps us see how money and laws play into marriage decisions.

## Third discussion point

Comparing today’s marriage trends with past data shows how younger folks view marriage differently now. This shift might reflect broader changes in how we see relationships and commitments.

## Weaknesses and next steps

Pointing out where our data might be off helps make our research more trust worthy. In the future, we could look deeper into why people choose certain times of the year to get married by tracking it over time or using detailed personal stories. Adding info like age or where people live could also give us a fuller picture of marriage trends.

\newpage

\appendix

# Appendix {-}


# Additional data details



\newpage


# References


